%-------------------------
% Resume in Latex
% Author : Biswajit Roy
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://biswajee.github.io}{\Large Biswajit Roy}} & Email : \href{mailto:roy.biswajeet161@gmail.com}{roy.biswajeet161@gmail.com}\\
  \href{https://biswajee.github.io}{https://biswajee.github.io} & Mobile : +91-9304005294 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Tata Consultancy Services}{Bangalore, India}
      {AWS Developer Intern}{Feb. 2020 - Mar. 2020}
      \resumeItemListStart
        \item
          {Responsible for building high-performing, scalable, enterprise-grade platform for AWS Migrations, AWS foundation and services maintainance and enhancements. Involved in using industry standard tools/platforms like Kubernetes (Container services).}
      \resumeItemListEnd

    \resumeSubheading
      {Tata Steel}{Jamshedpur, India}
      {Summer Trainee}{Jul. 2019 - Aug. 2019}
      \resumeItemListStart
        \resumeItem{\href{https://github.com/Biswajee/TMH_AutomationAPI}{Mobile and web team (TMH Vishwas)}}
          {Profiled and analysed existing application and discussed potential security issues with team.
          Developed API to help IOT devices connect to application.
          Employed Django REST framework to design REST APIs.
          Implemented OAuth2 authentication into application.
          Introduced REST for API development. Leveraged account verification process by 60\% using mobile verification and OAuth2. Estimated a 20\% growth of customers through API.}
      \resumeItemListEnd


          
    \resumeSubheading
      {FOSSEE 2019 IIT Bombay Summer Fellowship}{IIT Bombay, India}
      {Summer Intern, Fellow}{May. 2019 - Jun. 2019}
      \resumeItemListStart
        \resumeItem{\href{https://github.com/Biswajee/Collaboration}{Collaborative communities}}
          {Successfully created a django web application that involved 5 modules.
          Integrated features of unlimited document upload, image upload, presentation upload on server and displaying of the same in next window.
          Defined APIs that allows CRUD operation on MySQL database.
          Represented data visualization on Pantheon dataset using D3.js.
          Implemented multiple iterations of the prototype and presented them for evaluation.
          }
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Institute of Technology, Burdwan University}{}
      {Bachelor of Engineering in Computer Science and Engineering;  Percentage: 78.3\%.}{Aug. 2016 -- Aug. 2020}
    \resumeSubheading
      {TATA DAV School}{}
      {High school with Computer Science (minor); Percentage: 82.33\%.}{Mar. 2014 - Mar. 2016}
    \resumeSubheading
    {De Nobili School, F.R.I.}{}
    {Secondary school; Percentage: 87\%.}{Mar. 2003 - Mar. 2014}
  \resumeSubHeadingListEnd

\section{Awards and Recognition}
  \resumeSubHeadingListStart
   \resumeSubItem{\href{https://www.hackerrank.com/biswajitr}{Hackerrank}}{Bagged gold medals for problem solving, Java, C++ and silver medal for Python}
    \resumeSubItem{TCS Codevita 8}{Ranked 151 in zonal and overall 875 out of 55654 candidates}
    \resumeSubItem{Codechef - Alibaba Cloud API Hackathon (Ranked 23rd in 2285 teams)}
      {Directi, Intel, Alibaba Cloud, 2018}
    \resumeSubItem{Young Scientist Award}{University of Burdwan, 2018}
  \resumeSubHeadingListEnd
  
\section{Selected Open-Source Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/Last-leaf}{Lastleaf (Soracom Cellular IOT Challenge)}}
      {Lastleaf rescues from road accidents by sending automated SOS using Raspberry Pi, Android application, Soracom service and Internet. It was listed among the hardware winning ideas.}
    \resumeSubItem{\href{https://github.com/Biswajee/TeamSpeak}{TeamSpeak - Chat platform}}
      {TeamSpeak helps in event participation in collaborative way where one can discuss on topics. It integrates with Directi's Codechef as chat platform using Codechef OAuth2 API, Alibaba Cloud ECS and RDS. Implemented socket.io on Node.js and MongoDB. It is dockerized to run on cloud server.}
    \resumeSubItem{\href{https://www.hackathon.io/103687}{Pragati (AngelHack Jaipur 2018)}}
      {An Android application that enables needy people have a free meal.}
      \resumeSubItem{\href{https://github.com/Biswajee/PlagScan_NITJSR}{Plagiarism Scanner (TATA Crucible Hackathon 2018)}}
      {Coordinated a team of three to prepare a django web service that seamlessly integrates with TATA Crucible's platform and scan for plagiarized content in submissions using web scraping and NLP.}
  \resumeSubHeadingListEnd

\section{Relevant Skills Summary}
  \resumeSubHeadingListStart
    \resumeSubItem{Technologies}
        {C/C++, Java (Swing, Maven, Android), Python (Django, Django REST Framework, Flask), JavaScript (D3.js, JSON, Node.js), HTML5, Git, Docker, Firebase, MySQL, Oracle, SQLite, MongoDB, OAuth2, Scikit learn, Tensorflow, Keras, OpenCV.}
      \item{
     \textbf{Areas of Proficiency}{: Cloud computing, Web development, Image processing, Data analysis, Machine learning.}
    }
  \resumeSubHeadingListEnd
\end{document}